---
title: "Digital Scholarship: An Introduction"
pagetitle: "Digital Scholarship: An Introduction"
---

```{r echo=FALSE}
knitr::read_chunk("./scripts/workshop_files.R")
```

## Description

This workshop will briefly introduce:

* navigating using a terminal environment.
* basic markdown syntax and document structure.
* publishing markdown documents with GitHub pages.

## Objectives

* Introduce a set of computational tools used in academia for research and scholarly communication.
* Emphasize the role of these tools in transparency and reproducibility.
* Explore approaches to solving issues related to research and scholarly communication that leverage computational approaches.

## Outcomes

* Navigate a file system with the command line.
* Author a basic document with Markdown syntax.
* Understand the role of plain text authoring in the context of research and scholarly communication.
* Publish a Markdown document to the web using GitHub Pages.

## What you will need

* A computer. Neither a tablet nor cell phone will suffice.

## Pre-load

* Set up a [GitHub account](https://github.com/)
* Install [Atom](https://atom.io/)
* Set up a terminal
     - Mac and Linux: bash or zsh terminal apps are already installed
     - Windows: install _Windows Subsystem for Linux_ (WSL). Follow the instructions in the _Install_ section of <https://docs.microsoft.com/en-us/windows/wsl/install>. A bash prompt will open after installation is complete. To access bash again later open Command Prompt (Click Start, enter `cmd`, select Command Prompt), type `bash`, then hit enter.
    
<div class = "note">
If you see the error "Windows Subsystem for Linux has no distributions", run the command `wsl --install -d Ubuntu` in Command Prompt, wait for the Ubuntu distribution to download and install, then try again.
</div>

## Files

```{r loadfiles, results='asis', echo=FALSE}
```
